\pkg{partykit}: A Modular Toolkit for Recursive Partytioning in \proglang{R}

### 2015-02-20 pkg/partykit/inst/mloss/mloss2.Rnw
more details in addr
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@688 255f4249-2263-4417-b1ea-8498779e27a7

%% header declarations
\author{Torsten Hothorn \\ \addr{Universit\"at Z\"urich} \\ \addr{E-mail: Torsten.Hothorn@R-project.org} \AND
        Achim Zeileis \\ \addr{Universit\"at Innsbruck} \\ \addr{E-mail: Achim.Zeileis@R-project.org}}
\title{\pkg{partykit}: A Modular Toolkit for Recursive Partytioning in \proglang{R}}
\editor{Cheng Soon Ong}

>>>>

%% header declarations
\author{Torsten Hothorn \\ \addr{Institut f\"ur Epidemiologie, Biostatistik und Pr\"avention, Universit\"at Z\"urich} \\ \email{E-mail: Torsten.Hothorn@R-project.org} \AND
        Achim Zeileis \\ \addr{Department f\"ur Statistik, Universit\"at Innsbruck} \\ \email{E-mail: Achim.Zeileis@R-project.org}}
\title{\pkg{partykit}: A Modular Toolkit for Recursive Partytioning in \proglang{R}}
\editor{Cheng Soon Ong}
